---
title: "Visualizing Performance Counter Data with hpcvis"
author: "Drew Schmidt"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: true
    toc: true
    number_sections: true
    css: include/custom.css
    highlight: kate
bibliography: include/hpcvis.bib
csl: "include/ieee.csl"
vignette: >
  %\VignetteIndexEntry{Visualizing Performance Counter Data with hpcvis}
  %\VignetteEngine{knitr::rmarkdown}
---



```{r, echo = FALSE, message = FALSE}
library(hpcvis)

options(scipen = 3)
knitr::opts_chunk$set(
  comment = NA,
  error   = FALSE,
  tidy    = FALSE
)
```


# Introduction

hpcvis offers utilities for benchmarking and visualizing profiler data from MPI profilers, as well as performance counter data from PAPI.


[[@pbdR2012]]
[[@papipackage]]
[[@papivignette]]
[[@mucci1999papi]]





# Importing data

It is quite possible, or perhaps even likely, that the computing environment in which you wish to *analyze* performance counter data is very different from the one which will *produce* it.  Recall that the **pbdPAPI** package must run under a Linux environment, where you may not wish to deal with the headache of installing all of the dependencies of **hpcvis** (notably, **ggplot2**).

```r
x <- system.cache(rnorm(1e4))
x
## L1 Cache Misses: 5669
## L2 Cache Misses: 6910
## L3 Cache Misses: 3526 
```

```r
papiexport(x)
## x <-
## structure(list(`L1 cache misses` = 5669, `L2 cache misses` = 6910, 
##     `L3 cache misses` = 3526), .Names = c("L1 cache misses", 
## "L2 cache misses", "L3 cache misses"), class = c("papi_output", 
## "papi_cache"), call = "rnorm(10000)")
```

or even to a file

```r
dump("x", "/path/to/myfile")
```



# Hardware Profiler Data

```{r}
library(hpcvis)
file <- system.file("testdata/cache_misses.Rda", package="hpcvis")
load(file)
```

This loads three objects named `cm_1e4`, `cm_5e4`, and `cm_1e5`.

```{r, echo=TRUE, eval=TRUE}
cm_1e4
```


```{r, echo=TRUE, eval=TRUE}
papiplot(cm_1e4)
```


```{r, echo=TRUE, eval=TRUE}
papiplot(cm_1e4, cm_5e4, cm_1e5)
```



```{r, echo=TRUE, eval=TRUE}
papiplot(cm_1e4, cm_5e4, cm_1e5, color=TRUE, opnames=NULL)
```



```{r, echo=TRUE, eval=TRUE}
papiplot(cm_1e4, cm_5e4, cm_1e5, facet.by="level", label.angle=20) 
```


```{r, echo=TRUE, eval=TRUE}
papiplot(cm_1e4, cm_5e4, cm_1e5, color=TRUE, facet.by="level", label.angle=20)
```




# Benchmark Plotters

```{r, echo=TRUE, eval=TRUE}
library(hpcvis)
file <- system.file("testdata/cachebench.Rda", package="hpcvis")
load(file)
```

```{r, echo=TRUE, eval=TRUE}
papiplot(rnorm_cachebench)
papiplot(rnorm_cachebench, facet.by="operation", label.angle=15)
```




# Legal

&copy; 2016 Drew Schmidt.

Permission is granted to make and distribute verbatim copies of this vignette and its source provided the copyright notice and this permission notice are preserved on all copies.

Any opinions, findings, and conclusions or recommendations expressed in  this material are those of the authors and do not necessarily reflect the  views of the National Science Foundation.  The findings and conclusions in this article have not been formally disseminated by the U.S. Department of Health \& Human Services nor by the U.S. Department of Energy, and should not be construed to represent any determination or policy of University, Agency, Administration and National Laboratory.

This manual may be incorrect or out-of-date.  The authors assume no responsibility for errors or omissions, or for damages resulting from the use of the information contained herein.





# References
<script language="JavaScript" src="include/headers.js"></script>
