---
title: "Visualizing MPI Codes with hpcvis"
author: "Drew Schmidt"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: true
    toc: true
    number_sections: true
    css: include/custom.css
    highlight: kate
bibliography: include/hpcvis.bib
csl: "include/ieee.csl"
vignette: >
  %\VignetteIndexEntry{Visualizing MPI Codes with hpcvis}
  %\VignetteEngine{knitr::rmarkdown}
---



```{r, echo = FALSE, message = FALSE}
library(hpcvis)

options(scipen = 3)
knitr::opts_chunk$set(
  cache   = TRUE,
  comment = NA,
  error   = FALSE,
  tidy    = FALSE
)
```


# Introduction

In this vignette, we will introduce the facilities for visualizing MPI profiler data, as generated from the **pbdPROF** package [[@profpackage]].  Before proceeding, the reader is encouraged to start with the *Introducing hpcvis* vignette, which is distributed with the **hpcvis** package [[@hpcvis]].

Recall that **pbdPROF** supports both the **fpmpi** [[@fpmpi]] and **mpiP** [[@mpiP]] profilers for MPI.  The remaining sections are split between these two profilers.




# Plotting fpmpi Data

Since **fpmpi** profiler data is relatively simple, so too are the visualizations we can create from it.

Before proceeding, let us load some sample data.  We will use the **fpmpi** profiler output from a **pbdMPI** [[@pbdMPI]] code written in a "manager/worker" style, which computed quantiles of a random dataset.

```{r}
library(hpcvis)
file <- system.file("extdata/quantile.mw.fpmpi", package="pbdPROF")
quantile.fpmpi <- pbdPROF::read.prof(file)
```

To visualize, we need only call the `profplot()` function on our data:

```{r}
profplot(quantile.fpmpi)
```

Note the 4 different plots.  These should be self-explanatory for someone familiar with MPI, so we will not elaborate here on their meaning or value.  However, it may be that someone does not want or need all 4 plots.  We can easily subset them with an integer vector argument `which` passed to `profplot()`.  For example:

```{r}
profplot(quantile.fpmpi, which=1:2)
```

This gives us the first two plots (in order 1, 2).  We could use the vector `2:1` (the reverse) to display them in reverse order.

For **fpmpi**, only one of the remaining `profplot()` arguments is valid (i.e., not ignored), namely `title`.  By default, the plot "title" is "FPMPI Profiler Output".  We can pass our preferred title as a string, or remove the title entirely by passing `NULL`.  We show the latter as a simple example:

```{r}
profplot(quantile.fpmpi, which=2, title=NULL)
```





# Plotting mpiP Data

Compared to **fpmpi**, **mpiP** profiler data is significantly more complex.  Likewise, the visualizations we can create from it become more complex.

Before proceeding, let us load some sample data.  We will use the **fpmpi** profiler output from a **pbdMPI** [[@pbdMPI]] code written in a "manager/worker" style, which computed quantiles of a random dataset.

```{r}
library(hpcvis)
file <- system.file("extdata/quantile.mw.mpip", package="pbdPROF")
quantile.mpip <- pbdPROF::read.prof(file)
```


## Basic Usage

As before, we need only call the `profplot()` function on our data:

```{r}
profplot(quantile.mpip)
```

Basic plot options such as the `title` and `which` arguments work identically here as with **fpmpi** profiler data, and so we do not revisit their use here.  For examples, see the above section.


## Plot Type

Since **mpiP** offers quite a lot of information about the MPI codes, we separate our plots into different "types".  We currently have plots which give information about MPI timings, some simple statistics, and message sizes.  The different plot sets can be generated via the `plot.type` argument to `profplot()`, and the arguments are "timings", "stats", and "messages", respectively.  

The default plot type (shown in the subsection above) gives the "timings" plots, so we do not recreate it here.  We show the "messages" plots:

```{r}
profplot(quantile.mpip, plot.type="messages")
```


## Bars

There is some amount of customization available for the many barplots in any of the subplots in each of the above plot types.  For instance, by passing the argument `stacked=TRUE`, then the barplots will be stacked barplots (like a non-polar coordinate pie chart).  We show this for the "stats" plot type:

```{r}
profplot(quantile.mpip, plot.type="stats", stacked=TRUE)
```

Finally, we can also add bar labels by passing the argument `bar.label=TRUE`.  These labels will show the numerical value of the bar, which is not generally recommended, but some journals like this style.  We again show this for the "stats" plot type:

```{r}
profplot(quantile.mpip, plot.type="stats", which=1, bar.label=TRUE)
```

The various options are designed to interact with each other in a reasonably smooth way.  For example, if we pass `stacked=TRUE` and `bar.label=TRUE` together, then the values are summed:

```{r}
profplot(quantile.mpip, plot.type="stats", which=2, stacked=TRUE, bar.label=TRUE)
```





# Legal

&copy; 2016 Drew Schmidt.

Permission is granted to make and distribute verbatim copies of this vignette and its source provided the copyright notice and this permission notice are preserved on all copies.

Any opinions, findings, and conclusions or recommendations expressed in  this material are those of the authors and do not necessarily reflect the  views of the National Science Foundation.  The findings and conclusions in this article have not been formally disseminated by the U.S. Department of Health \& Human Services nor by the U.S. Department of Energy, and should not be construed to represent any determination or policy of University, Agency, Administration and National Laboratory.

This manual may be incorrect or out-of-date.  The authors assume no responsibility for errors or omissions, or for damages resulting from the use of the information contained herein.





# References
<script language="JavaScript" src="include/headers.js"></script>
